\textbf{Response Letter}

### 2018-12-25 doc/aij18/major-revision/letter.tex
last update Dec 25 13:37

>>>>

\textcolor{blue}{The figures that appear in the third column of Table 3 for each learning system were taken from the respective published papers. They all refer to the specific experimental setup used in the evaluation of the approaches. In general, since there is not a common benchmark for the evaluation of learning approaches, each system selects the configuration of training data that best adapts to the particularities of the approach. Hence, all the figures in the 3rd column of Table 3 refer to the specific implementation used in the experiments. What we tried to do in this section is to somehow compare the approaches by establishing some common patterns of evaluation, namely number of tested domains, size of the training data in terms of action and/or traces, degree of observability, etc.}
